---
title: "usAirData Package"
author: "Alexis Nguyen"
date: "2025-11-30"
output: html_document
---
## R Markdown

```{r setup, message=FALSE}
# load my package while I am working on it
devtools::load_all()
```

## About This Package

This package uses a US airline cost dataset and it includes three functions I added that:
- Calculates the average cost
- Finds the row with the highest cost
- Shows a plot that shows cost over time
I chose this dataset becaise it was easy for me to work with and I also enjoy the topic because it is related to travel and airlines. This made it more interesting. This ptoject helped me learn more about R and how creating a package goes, and how to add my own details and pizzazz.

## Loading the Dataset

```{r}
data(airdata)
head(airdata)
```

This shows the first few rows of the dataset which can make sure it loads in.

## Average Cost Function

```{r}
avg_cost(airdata)
```

This functions calculates the average cost to the entire dataset.

## Highest Cost Row

```{r}
highest_cost(airdata)
```

This function finds the row with the highest cost value.

## Plot of Cost Over Time

```{r}
plot_cost_over_time(airdata)
```

This function makes a line plot that shows how cost changes over the years.

## Reflection 

This project helped me learn how to build a simple R package while adding my own elements to it.During this project I got to implement something I find interesting and enjoyable so it made the project go by faster. It was somewhat confusing at first, but everything came together at the end.
